Mechanising Hylomorphisms for Extraction of Executable Code

### 2025-03-24 paper/paper.tex
Fix
minor

\subsection{Mechanising Extractable Container Functors}
\label{sec:containers}

A direct encoding of containers as presented in
Section~\ref{sec:category-theory} requires the use of the functional
extensionality axiom, and axiom K to deal with equalities of objects of type
$P(s) \to X$. Furthermore, extraction will need to insert unsafe casts for
anything of type $P(s)$.  To avoid these problems, we use \emph{setoids}, and
encode families of positions using \emph{decidable validity predicates}.

In our formalisation, we require that every type is a setoid, where \coq{x =e y}
denotes setoid equality. All morphisms need to be \emph{proper} morphisms that
respect setoid equalities. We use special notation for such morphisms, \coq{A ~>
  B}, and we add an implicit coercion from \coq{A ~> B} to \coq{A -> B}.  We
also provide tactics to automatically discharge proofs that morphisms are
proper,  for some simple cases.

>>>>

\subsection{Mechanising Extractable Container Functors}
\label{sec:containers}
A direct encoding of containers as presented in
Section~\ref{sec:category-theory} requires the use of the functional
extensionality axiom, and axiom K to deal with equalities of objects of type
$P(s) \to X$. Furthermore, upon extraction Coq will need to insert unsafe casts for
anything of type $P(s)$.  To avoid these problems, we use \emph{setoids}, and
encode families of positions using \emph{decidable validity predicates}.

In our formalisation, we require that every type is a setoid, where \coq{x =e y}
denotes setoid equality and that all morphisms need to be \emph{proper}
morphisms that respect setoid equalities. We use special notation  \coq{A ~> B}
for proper morphisms and we add an implicit coercion from \coq{A ~> B} to \coq{A -> B}.  We also provide tactics to automatically discharge proofs that morphisms are proper,  for some simple cases.
